Weather Data Integration and Assimilation System\\

### 2020-02-09 introduction/sec_1-motivation.tex
Minor changes

\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

\dbc{Saying something proprietary is not good reason to do research. You should highlight the context under which these solutions are developed and differences between CUrW and Sri Lanka in general. Also, give a bit more details than saying "to cater to their country-specific requirements". All key systems such as DIAS, MADIS, Delf, etc. need to be properly cited.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrfull{nwm}. These NWMs utilize \db{multimodal} weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Minor changes

\section{Problem Statement}
Handling spatio-temporal weather data is challenging. Need an extendable system to support weather models by efficiently storing and retrieving data. Therefore, in this context the problem can be state as;
\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
interact with different data formats including spatio-temporal bulk stream data, 
store efficiently while optimizing the disk space,
support geographical and time-base queries,
third parties can access the data with easy integration, and
able to easy modify and use based on the requirements.
}

>>>>

\section{Problem Statement}
Handling spatio-temporal weather data is challenging. Need an extendable system to support weather models by efficiently storing and retrieving data. Therefore, in this context the problem can be state as;

\emph{necessaty of a Data Integration System which is scalable, highly available and capable of }
\emph{interact with different data formats including spatio-temporal bulk stream data, }
\emph{store efficiently while optimizing the disk space, }
\emph{support geographical and time-base queries, }
\emph{third parties can access the data with easy integration, and }
\emph{able to easy modify and use based on the requirements.}
